TITLE

### 2021-02-26 outputs/Paper.Rmd
update

# Data 
In this report, we use the R statistical programming language [@citeR]. To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1] ADD ANY PACKAGE HERE. The survey conducted by Petit Poll collects the following data:

@@

```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=10, fig.height=10}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-simulated_data[-c(1,2)] #Remove Type and postcode columns

@@

>>>>

# Data 
In this report, we use the R statistical programming language [@citeR]. To be specific, we use the “tidyverse” package to process data [@citetidyverse], "kableExtra" package to generate tables [@citekableExtra],  "ggplot2" is used to draw diagrams [@gg1], "ggthemes" is used to change the diagram theme. [@themes]ADD ANY PACKAGE HERE. The survey conducted by Petit Poll collects the following data:

@@

```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=10, fig.height=10}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-simulated_data[-c(1,2)] %>% #Remove Type and postcode columns
rename(
  Region = Q2,
  operation_years = Q5,
  Hourly_rate = Q9,
  Total_renvenue =Q13,
  Type=Q3,
  Fanchise= Q4,
  Takeout=Q6,
  Delivery=Q7,
  Size=Q8,
  COVID = Q10,
  Fixed=Q11,
  Flex=Q12
)

@@

Dummy_data<-   # change column names
  Dummy_data
